---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

```{r}
setwd('/Users/public/Downloads')
s_file <- read.csv('activity.csv')
```

```{r}
s_file[!complete.cases(input_file),]
data <- na.omit(s_file)
```

## What is mean total number of steps taken per day?
```{r}
a <- 0
f_data1 <- data.frame(x = numeric(61), y = character(61),stringsAsFactors=FALSE)
for ( i in levels(data$date) ) {
        data1 <- subset(data,data$date==i)
        f_data1$x[a] <- (sum(data1$steps))
        f_data1$y[a] <- i
        a <- a + 1
         }
colnames(f_data1) <- c("sum_of_steps_for_Each_day", "date")
hist(f_data1$sum_of_steps_for_Each_day)
```

```{r}

mean(f_data1$sum_of_steps_for_Each_day)
median(f_data1$sum_of_steps_for_Each_day)
```

## What is the average daily activity pattern?
### Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis) ###

```{r}
a <- 0
f_data2 <- data.frame(x = numeric(288), y = numeric(288))
for ( i in unique(data$interval) ) {
         data2 <- subset(data,data$interval==i)
         f_data2$x[a] <- (sum(data2$steps))/nrow(data2)
         f_data2$y[a] <- i
         a <- a + 1
         }
colnames(f_data2) <- c("average_steps_for_each_interval", "interval")
plot(f_data2$interval,f_data2$average_steps_for_each_interval)
```

### Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps? ###

```{r}
max(f_data2$average_steps_for_each_interval)
subset(f_data2,f_data2$average_steps_for_each_interval>206)
```


## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
